A Unification of Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-01-22 colt-21/cvx-flats.tex
Merging Lemmas and changing P codimension to d representation(Definitely missed some spots on the latter though)

\begin{definition}[$\P$-codimension]
	The \emph{\Pcodimension} of a convex set $F \subseteq \P$ is the minimum $d$ such that there exists a measurable function $V : \Y \to \reals^d$ such that $F = \zeros{V}$, and is denoted $\Pcodim(F)$.
\end{definition}

@@

\begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
Let target property $\gamma:\P \toto \R$ and $d\in\mathbb N$ be given.
Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
If there is no flat $F$ of \Pcodimension at most $d$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
%  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$, indirectly elicited by a convex loss $L \in \L_d$.
%  For all $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
%  In particular, if there is a $p \in \P$ such that $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{thm:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
	Moreover, by construction of such a flat, we know the \Pcodimension is at most $d$.
	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
	Thus, we have $p \in F \subseteq \gamma_r$.

@@

\begin{corollary}\label{cor:Pcodim-flat-elic-relint-prop} 
  Let an elicitable target property $\gamma:\P \toto \R$ be given, where $\P\subseteq\simplex$ is defined over a finite set of outcomes $\Y$, and let $d\in\mathbb N$.
Let $p \in \relint{\P}$.
If there is no flat $F$ of \Pcodimension at most $d$ with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
%
%  %commented out 20 Jan 2021 at 8:40a - Jessie - switching first statement to be the contrapositive.
%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$ for a finite set of outcomes $\Y$, indirectly elicited by a convex loss $L \in \L_d$.
%	For all $p \in \relint{\P}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
%	Moreover, if there is some $p \in \relint{\P}$ so that there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$, and suppose $r' = \psi(u)$.
	Take $F \subseteq \Gamma_u$ to be the flat that exists by Lemma~\ref{thm:convex-flats-inf-dim}.
	If $r = r'$, then $p \in F \subseteq \Gamma_u \subseteq \gamma_r$ by indirect elicitation.
	Otherwise, by Lemma~\ref{lem:set-valued-prop-flats}, for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, we observe $p \in F\subseteq \gamma_r \iff p \in F \subseteq \gamma_{r'}$.

@@

\begin{lemma}\label{lem:finite-relint-dim}
  Let flat $F\subseteq \P$ contain some $p\in\relint{\P}$.
  Then $p \in \relint{F}$ and $\Pcodim(F) = \codim(F)$.
\end{lemma}
\begin{proof}
	\jessie{TODO}
	First, to observe $p \in \relint{F}$, since $p \in \relint{\P}$, we must have some ball $B(\epsilon, p) \subseteq \P$ so that $B(\epsilon, p) \cap F \subseteq F$ and is also a ball, and thus $p \in \relint{F}$.

	Moreover, to observe $\Pcodim(F) = \codim(F)$, \jessie{TODO}
\end{proof}

@@

\subsection{Reconstructing the result of~\citet[Theorem 16]{ramaswamy2016convex}}
\begin{lemma}\label{lem:feas-sub-is-a-flat}
	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
	If $F$ is a flat so that $p \in F \subseteq \gamma_r$, then $F - p$ is a subspace contained in $\Sc_{\gamma_r}(p)$.
	\jessie{Is this what we want to show? I feel like we want $\Sc_{\gamma_r}(p)$ is a flat containing $p$.}  
	%  \raf{I think you want $p$ in the interior of the simplex for now}
\end{lemma}
\begin{proof}
	First, observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$ (since $F$ contains $p$, which we subtract from).
	Moreover, by Lemma~\ref{lem:finite-relint-dim}, we have $p \in \relint(F)$, so $\vec 0 \in \relint{F-p}$.

% %commented out 01.21.2021 - Jessie
%	\jessie{Revisit this proof}
%	Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$ (since $F$ contains $p$, which we subtract from).
%	Now consider $v \in F - p$.
%	Since $p \in \relint{\P}$, there is an open ball of radius $\epsilon$ in the span of $\P$ so that for all $q \in B(p, \epsilon)$, we have $q \in \P$.
%	In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \P$.
%	Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
%	Since level sets of elicitable properties are convex (\citep{lambert2009eliciting}) this is true for all $\alpha' \in [0,\alpha]$.
%	Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
\end{proof}

The next result helps us generalize Lemma~\ref{lem:feas-sub-is-a-flat} to any $p$; not just to $p \in \relint{\P}$.
\newcommand{\simplexp}{\Delta_{\Y'}}
\begin{lemma}\label{lem:p-boundary-fsd}
	For any $p \in \P$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp \cap \P$.
	Then $\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p))$.
\end{lemma}
\begin{proof}
	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.

	Now to see $\dim(\Sc_{\gamma_r}(p)) \leq \dim(\Sc_{\gamma'_r}(p))$, it suffices to show subset inclusion.
	Take some $v \not \in \Sc_{\gamma'_r}(p)$.
	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$, it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp \cap \P$ means one of $q^\pm$ also is not in $\P$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \P$.
	Thus $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
	%commented out 05.26.2020
	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
	%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
	%	\begin{align*}
	%	\dim(\Sc'_{\gamma_r}(p)) &= \dim(\Sc_{\gamma_r}(p)) + \dim(P) - \dim(\Sc_{\gamma_r}(p) + P)
	%	\end{align*}
	%	If $\dim(P) = \dim(\Sc_{\gamma_r}(p) + P)$, the claim holds.
	%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\Sc_{\gamma_r}(p) + P) = \|p\|_0$.		
	%	One way to do this is to show $\Sc_{\gamma_r}(p) \subseteq P$.
	%	
	%	Suppose there was some $v \not\in P$ such that $v \in \Sc_{\gamma_r}(p)$.
	%	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
	%	However, if $v \in \Sc_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
	%	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
	%	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
	%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \Sc_{\gamma_r}(p)$.
	%	Therefore, $\Sc_{\gamma_r}(p) \subseteq P$, and $\dim(\Sc_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
\end{proof}

@@

	As $L'$ is calibrated with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Theorem~\ref{thm:cvx-flats}, we know there exists a flat $F' \subseteq$ of codimension $d$ relative to $\reals^{\Y'}$ so that $\codim(F') \leq d$.
	Moreover, as $d$ is the maximal codimension of such a flat, we show in Lemma~\ref{lem:feas-sub-is-a-flat} that $\Sc_{\gamma_r}(p)$ is one such flat, and we have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq \|p\|_0 - d- 1$.
	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and from there we observe the result.
	%	First, for intuition, consider $p \in \relint{\simplex}$. 
	%	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
	%	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\Sc_{\gamma_r}(p)) - 1$.
	%
	%	
	%	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
	%	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and thus the result holds.
	%	
	%	Now to see that $L'$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$,
	%	\begin{align*}
	%		\forall p \in \Delta_{\Y'}:  \inf_{u \in \reals^d : \psi(u) \not \in \gamma'(p)} L'(u;p) = \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p) = \inf_{u \in \reals^d} L'(u;p)~.~
	%	\end{align*}
	%	Therefore, we have $L'$ calibrated with respect to $\ell'$.
	%
	%	Moreover, we want to show $L'$ indirectly elicits $\gamma'$ so we can apply Theorem~\ref{thm:cvx-flats}.
	%	First, observe that $L'$ elicits $\Gamma' : p \mapsto \Gamma(p)$ for all $p \in \Delta_{\Y'}$ 
	%	For all $p \in \simplex$, we have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
	%	As $\Delta_{\Y'} \subseteq \simplex$, this is in particular true for all $p \in \Delta_{\Y'}$.
	%	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.
\end{proof}

>>>>

\begin{definition}[$d$-representation]
	The flat $F \subseteq \P$ is a $d$-representation if there exists a measurable function $V : \Y \to \reals^d$ such that $F = \zeros{V}$.
\end{definition}

@@

\begin{corollary}\label{cor:Pcodim-flat-single-val-prop}
Let target property $\gamma:\P \toto \R$ and $d\in\mathbb N$ be given.
Let $p \in \P$ with $|\gamma(p)| = 1$, and take $\gamma(p) = \{r\}$.
If there is no flat $F$ that is a $d$-representation with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
%  %commented out 20 Jan 2021 8:37am - Jessie.  switching first statement to be the contrapositive
%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$, indirectly elicited by a convex loss $L \in \L_d$.
%  For all $p \in \P$ with $|\gamma(p)| = 1$, and $\gamma(p) = \{r\}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
%  In particular, if there is a $p \in \P$ such that $\gamma(p) = \{r\}$ such that there is no flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$, then there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$.
	Since $\gamma$ is single-valued at $p$, we have $r = \psi(u)$; by Lemma~\ref{thm:convex-flats-inf-dim}, we know there is a flat $F = \zeros{V_{u,p}}$ so that $p \in F \subseteq \Gamma_u$.
	Moreover, by construction of such a flat, we know it is a $d$-representation.
	By definition of indirect elicitation, we additionally have $\Gamma_u \subseteq \gamma_r$.
	Thus, we have $p \in F \subseteq \gamma_r$.

@@

\begin{corollary}\label{cor:Pcodim-flat-elic-relint-prop} 
  Let an elicitable target property $\gamma:\P \toto \R$ be given, where $\P\subseteq\simplex$ is defined over a finite set of outcomes $\Y$, and let $d\in\mathbb N$.
Let $p \in \relint{\P}$.
If there is no flat $F$ of that is a $d$-representation with $p \in F \subseteq \gamma_r$, then no $L\in\L_d$ indirectly elicits $\gamma$, and in particular, there is no convex surrogate $L \in \L_d$ consistent with respect to $\gamma$.
%
%  %commented out 20 Jan 2021 at 8:40a - Jessie - switching first statement to be the contrapositive.
%  Suppose we are given a target property $\gamma:\P \toto \R$, where $\P\subseteq\simplex$ for a finite set of outcomes $\Y$, indirectly elicited by a convex loss $L \in \L_d$.
%	For all $p \in \relint{\P}$, there is some flat $F$ of \Pcodimension at most $d$ such that $p \in F \subseteq \gamma_r$.
%	Moreover, if there is some $p \in \relint{\P}$ so that there is not a flat $F \subseteq \gamma_r$ of \Pcodimension at most $d$ then there is no $d$-dimensional convex surrogate $L$ consistent with respect to $\gamma$.
\end{corollary}
\begin{proof}
	Let $(L, \psi)$ indirectly elicit $\gamma$ and the convex function $L$ and elicit $\Gamma$.
	As $\Gamma$ is non-empty, there is some $u \in \Gamma(p)$, and suppose $r' = \psi(u)$.
	Take $F \subseteq \Gamma_u$ to be the flat that exists by Lemma~\ref{thm:convex-flats-inf-dim}.
	If $r = r'$, then $p \in F \subseteq \Gamma_u \subseteq \gamma_r$ by indirect elicitation.
	Otherwise, by Lemma~\ref{lem:set-valued-prop-flats}, for elicitable properties with $p \in \gamma_r \cap \gamma_{r'}$, we observe $p \in F\subseteq \gamma_r \iff p \in F \subseteq \gamma_{r'}$.

@@

\begin{lemma}\label{lem:finite-relint-dim}
  Let flat $F\subseteq \P$ that is a $d$-representation containing some $p\in\relint{\P}$.
  Then 
  \begin{enumerate}
  	\item $p \in \relint{F}$; 
  	\item $\dim(\spn(F - \{p\})) \geq \dim(\spn(\P - \{p\})) - d$;
  	\item Given a discrete elicitable property $\gamma: \P \toto \R$ and $r \in \gamma(p)$, we have $F - \{p\}$ contained in $\Sc_{\gamma_r}(p)$.
  \end{enumerate}
\end{lemma}
\begin{proof}

	(1.)
	Since $p \in \relint{\P}$, there is some small enough $\epsilon > 0 $ so that for $q \in \P, \alpha \in (-\epsilon,\epsilon)$, the point $q_\alpha := p - \alpha(q - p)$ is still in $\P$.
	In particular, for $q \in F$, then $q_\alpha \in F$, as it is a linear combination of elements of $F$, which is a convex set as it is a flat.
	Therefore, $p \in \relint{F}$.

	\bigskip

	(2.)
	Let $p \in \relint{\P} \cap F$, and define $F_p := F - \{p\}$, $\P_p := \P - \{p\}$ and $T_W(v) = \E_{Y \sim v} W(Y)$ for that function $W : \Y \to \reals^d$ such that $F = \zeros{W}$.
	(Such a function must exist by $F$ being a $d$-representation.)

	Now let $v \in \ker(T_W) = \{v \in \spn(\P_p) : T_W(v) = \vec 0\}$.
	There must exist an $\epsilon > 0$ so that $\epsilon v \in F_p$ and $-\epsilon v \in F_p$ since, by (1.), we have $p \in \relint{\P}$, and therefore $\vec 0 \in \relint{F_p}$.
	Moreover, we have $\pm \epsilon v \in \ker(T_W)$ by linearity of expectation, so $v \in \relint{\ker(T_W)}$.
	This allows us to conclude $\spn(F_p) = \ker(T_W)$.\jessie{Right?}

	We want to show $F_p = \P_p \cap \ker(T_W)$, then derive the result from there.

	In order to see this, consider $v \in F_p \iff v + p \in F$, and similarly for $\P_p$.
	Now, as $F \subseteq \P$ by construction, we have $F_p \subseteq \P_p$, and since $\spn(F_p) = \ker(T_W)$, we additionally have $F_p \subseteq \ker(T_W)$, yielding $F_p \subseteq \P_p \cap \ker(T_W)$.
	Now consider $v \in \P_p \cap \ker(T_W)$; we know that $\E_v W = \vec 0$, and therefore, $\E_{q} W = \vec 0$, so $v \in F_p$, thus $F_p = \P_p \cap \ker(T_W)$.

	Since $\spn(F_p) = \ker(T_W)$, we have $\dim(\spn(F_p)) = \dim(\ker(T_W)) \geq \dim(\spn(\P_p)) - d$ by \jessie{isomorphism theorem} since $F_p = \ker(T_W) \cap \P_p$.

	\bigskip

	(3.)
	We aim to show $v \in F_p \implies v \in \Sc_{\gamma_r}(p)$.
	First, observe $v \in F_p \iff p + v \in F$.
	As $p \in \relint{\P}$, by part (1.), we additionally have $p \in \relint{F}$, and in turn $\vec 0 \in \relint{F_p}$.

	Suppose $v \in F_p$, and since $p \in \relint{F}$, there is an $\epsilon > 0$ so that for all $\alpha \in (-\epsilon, \epsilon)$, we have $p + \alpha v \in F \implies p + \alpha v \in \gamma_r$, since $F$ is convex.%, as are level sets of elicitable properties~\cite{lambert2009eliciting}.
	The result follows by applying the definition of Feasible Subspaces.	
\end{proof}

@@

\subsection{Reconstructing the result of~\citet[Theorem 16]{ramaswamy2016convex}}
%\begin{lemma}\label{lem:feas-sub-is-a-flat}
%	Suppose we have the discrete elicitable property $\gamma$ and distribution $p \in \relint{\simplex}$ with $r \in \gamma(p)$.
%	If $F$ is a flat so that $p \in F \subseteq \gamma_r$, then $F' := F - \{p\}$ is contained in $\Sc_{\gamma_r}(p)$.
%	%  \raf{I think you want $p$ in the interior of the simplex for now}
%\end{lemma}
%\begin{proof} \jessie{Better to combine; not currently using this}
%	We aim to show $v \in F' \implies v \in \Sc_{\gamma_r}(p)$.
%	First, observe $v \in F' \iff p + v \in F$.
%	As $p \in \relint{\simplex}$, by Lemma~\ref{lem:finite-relint-dim}, we additionally have $p \in \relint{F}$, and in turn $\vec 0 \in \relint{F'}$.
%	
%	Suppose $v \in F'$, and since $p \in \relint{F}$, there is an $\epsilon > 0$ so that for all $\alpha \in (-\epsilon, \epsilon)$, we have $p + \alpha v \in F \implies p + \alpha v \in \gamma_r$, since $F$ is convex.%, as are level sets of elicitable properties~\cite{lambert2009eliciting}.
%	The result follows by applying the definition of Feasible Subspaces.
%	%By definition of $\Sc_{\gamma_r}(p)$, there is then an $\epsilon$ satisfying the requirement for $v \in \Sc_{\gamma_r}(p)$, so we can conclude $v \in \Sc_{\gamma_r}(p)$, yielding the desired result.
%	
%% %commented out 01.21.2021 - Jessie
%%	\jessie{Revisit this proof}
%%	Observe $F-p$ is a subspace as it is a linear shift of $F$, which is a linear subspace by definition of a flat and the fact that it contains $\vec 0$ (since $F$ contains $p$, which we subtract from).
%%	Now consider $v \in F - p$.
%%	Since $p \in \relint{\P}$, there is an open ball of radius $\epsilon$ in the span of $\P$ so that for all $q \in B(p, \epsilon)$, we have $q \in \P$.
%%	In particular, take $\alpha = \epsilon / 2$, and we observe $p \pm \alpha v \in B(p, \epsilon)$, and therefore $p \pm \alpha v \in \P$.
%%	Moreover, by the assumption $v \in F - p$, we also have $p \pm \alpha v \in \gamma_r$. 
%%	Since level sets of elicitable properties are convex (\citep{lambert2009eliciting}) this is true for all $\alpha' \in [0,\alpha]$.
%%	Therefore, we observe $v \in S_{\gamma_r}(p)$, so $F-p \subseteq S_{\gamma_r}(p)$.
%\end{proof}

The next result helps us generalize Lemma~\ref{lem:feas-sub-is-a-flat} to any $p$; not just to $p \in \relint{\P}$.
\newcommand{\simplexp}{\Delta_{\Y'}}
\begin{lemma}\label{lem:p-boundary-fsd}
	For any $p \in \P$ and $r$ such that $p \in \gamma_r$, take $\Y' := \supp(p)$.
	Define $\gamma' : \P \toto \R$ with $\gamma' : q \mapsto \gamma(q) \cap \simplexp$.
	Then $\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p))$.
\end{lemma}
\begin{proof}
	Consider the ambient space of both $\Sc_{\gamma_r}(p)$ and $\Sc_{\gamma'_r}(p)$ is $\reals^\Y$.
	We trivially have $\dim(\Sc_{\gamma_r}(p)) \geq \dim(\Sc_{\gamma'_r}(p))$ since $\gamma'$ is simply $\gamma$ projected down to an affine subspace of $\reals^\Y$.

	Now to see $\dim(\Sc_{\gamma_r}(p)) \leq \dim(\Sc_{\gamma'_r}(p))$, it suffices to show subset inclusion.
	Take some $v \not \in \Sc_{\gamma'_r}(p)$.
	Observe that $\gamma'_r = \gamma_r \cap \simplexp$, so if $q^\pm := p \pm \epsilon v \not \in \gamma'_r$ for all $\epsilon > 0$, it is either because one of $q^+$ or $q^-$ is not in $\gamma_r$ or because either $q^\pm \not \in \simplexp$.
	The first case can be seen easily by the definition of $\gamma'$, and the latter can be seen because leaving $\simplexp$ means one of $q^\pm$ also is not in $\P$, and therefore not in $\gamma_r$ as $\gamma_r \subseteq \P$.
	Thus $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
	%commented out 05.26.2020
	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
	%	Consider $P := \spn(\{e_y : y \in \supp(p) \})$.
	%	\begin{align*}
	%	\dim(\Sc'_{\gamma_r}(p)) &= \dim(\Sc_{\gamma_r}(p)) + \dim(P) - \dim(\Sc_{\gamma_r}(p) + P)
	%	\end{align*}
	%	If $\dim(P) = \dim(\Sc_{\gamma_r}(p) + P)$, the claim holds.
	%	Be definition of $P$, we know $\dim(P) = \|p\|_0$, so we can show $\dim(\Sc_{\gamma_r}(p) + P) = \|p\|_0$.		
	%	One way to do this is to show $\Sc_{\gamma_r}(p) \subseteq P$.
	%	
	%	Suppose there was some $v \not\in P$ such that $v \in \Sc_{\gamma_r}(p)$.
	%	That means there is some $i$ so that $i \not \in \supp(p)$ (i.e. $p_i = 0$) but $v_i \neq 0$. \jessiet{Check this line.}
	%	However, if $v \in \Sc_{\gamma_r}(p)$, then there is some $\epsilon_0 > 0$ so that $p + \epsilon v$ and $p - \epsilon v \in \gamma_r \subseteq \simplex$ for all $\epsilon \in (0, \epsilon_0)$.
	%	For simplicity, consider $\epsilon = \epsilon_0 / 2$.
	%	Since $p_i = 0$, this gives $(p+\epsilon v)_i = (\epsilon v)_i$, and likewise for $(p - \epsilon v)_i$.
	%	As neither $\epsilon$ nor $v_i$ are $0$, one of these terms must be negative, and therefore not in the simplex.
	%	As $\gamma_r \subseteq \simplex$, we then have $v \not \in \Sc_{\gamma_r}(p)$.
	%	Therefore, $\Sc_{\gamma_r}(p) \subseteq P$, and $\dim(\Sc_{\gamma_r}(p) + P) = \dim(P) = \|p\|_0$.
\end{proof}

@@

	As $L'$ is calibrated (and consistent) with respect to $\ell'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then by Corollary~\ref{cor:Pcodim-flat-elic-relint-prop}, we know there exists a flat $F$ with $p \in F \subseteq \gamma'_r$ that is a $d$-representation.

	When we substitute $P = \simplexp$ into Lemma~\ref{lem:finite-relint-dim}, we yield $\dim(\spn(F_p)) \geq \dim(\spn(P_p)) - d$.
	Moreover, we can observe that $F_p \subseteq \Sc_{\gamma'_r}(p)$ since $p \in \relint{F}$, and in turn $\vec 0 \in \relint{F_p}$, and applying the definition of feasible subspace dimension.
	By Lemma~\ref{lem:p-boundary-fsd}, we additionally have $\Sc_{\gamma_r}(p) = \Sc_{\gamma'_r}(p)$.
	Chaining these results, we obtain $\dim(\Sc_{\gamma_r}(p)) = \dim(\Sc_{\gamma'_r}(p)) \geq \dim(\spn(F_p)) \geq \|p\|_0 - 1 - d$.

%	this yields the bound $\dim(\spn(F-\{p\})) \geq \|p\|_0 - 1 - d$.
%	Chaining inequalities, we then have $\dim(\Sc_{\gamma'_r}(p)) \geq \dim(\spn(F - \{p\})) \geq \|p\|_0 - d- 1$ as Lemma~\ref{lem:feas-sub-is-a-flat} states $F - \{p\}$ is a subspace of $\Sc_{\gamma'_r}(p)$.
%	Lemma~\ref{lem:p-boundary-fsd} then states $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and from there we observe the result.
	%
	%
	%\old version of the proof from NeurIPS or before - 01.21.2021
	%	First, for intuition, consider $p \in \relint{\simplex}$. 
	%	Theorem~\ref{thm:cvx-flats} implies that there exists a flat $F'$ of affine dimension at least $n-d-1$.
	%	Lemma~\ref{lem:feas-sub-is-a-flat} then says that $\dim(\Sc_{\gamma_r}(p)) \geq \dim(F') \geq n-d-1 \implies d \geq n - \dim(\Sc_{\gamma_r}(p)) - 1$.
	%
	%	
	%	If we can show that $L' := L|_{\Y'}$ is calibrated with respect to $\ell' := \R \times \Y' \to \reals$ with $\ell(r,y) = \ell'(r,y)$ for all $r \in \R$ and $y \in \Y'$ and indirectly elicits $\gamma' := \prop{\ell'}$, then we observe the existence of a flat $F^*$ of codimension $d$ (in $\reals^{\Y'}$) so that $\dim(F^*) = \|p\|_0 - d - 1$ by Theorem~\ref{thm:cvx-flats}.
	%	Then we can use Lemma~\ref{lem:p-boundary-fsd} to observe $\dim(\Sc_{\gamma'_r}(p)) = \dim(\Sc_{\gamma_r}(p))$, and thus the result holds.
	%	
	%	Now to see that $L'$ is calibrated with respect to $\ell'$, consider that $\gamma(p) = \gamma'(p)$ for all $p \in \Delta^{\Y'}$,
	%	\begin{align*}
	%		\forall p \in \Delta_{\Y'}:  \inf_{u \in \reals^d : \psi(u) \not \in \gamma'(p)} L'(u;p) = \inf_{u \in \reals^d : \psi(u) \not \in \gamma(p)} L(u;p) > \inf_{u \in \reals^d} L(u;p) = \inf_{u \in \reals^d} L'(u;p)~.~
	%	\end{align*}
	%	Therefore, we have $L'$ calibrated with respect to $\ell'$.
	%
	%	Moreover, we want to show $L'$ indirectly elicits $\gamma'$ so we can apply Theorem~\ref{thm:cvx-flats}.
	%	First, observe that $L'$ elicits $\Gamma' : p \mapsto \Gamma(p)$ for all $p \in \Delta_{\Y'}$ 
	%	For all $p \in \simplex$, we have $u \in \Gamma(p) \implies \psi(u) \in \gamma(p)$.
	%	As $\Delta_{\Y'} \subseteq \simplex$, this is in particular true for all $p \in \Delta_{\Y'}$.
	%	Therefore, for all $p \in \Delta_{\Y'}$, we have $\Gamma'_u = \Gamma_u \cap \Delta_{\Y'} \subseteq \gamma_{\psi(u)} \cap \Delta_{\Y'} = \gamma'_{\psi(u)}$, and thus $L'$ indirectly elicits $\gamma'$.
\end{proof}
